### 2016-05-13 2016-lrec-tyvmorph/poster.tex
authors updates
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68353 72bbbca6-d526-0410-a7d9-f06f51895060

	\begin{poster}{
		grid=false,
		%eyecatcher=false,
		borderColor=bordercol,
		headerColorOne=iumidnight,
		headerColorTwo=iumidnight,
		%headerColorOne=blue,
		headerFontColor=white,
		% Only simple background color used, no shading, so boxColorTwo isn't necessary
		boxColorOne=boxcolor,
		headershape=roundedright,
		headerborder=open,
		headerheight=0.1\textheight,
		%headershape=roundedright,
		%headershade=plain,
		%headerfont=\Large\textsf, %Sans Serif
		%headerfont=\Large\sf\bf,
		textborder=rectangle,
		%background=plain,
		%background=user,
		background=none,
		headerborder=open,
		boxshade=plain,
		textborder=roundedleft,
		columns=4,
	}{ %Eye Catcher, empty if option eyecatcher=false - unused
		\includegraphics[height=6.5em]{uitlogo}
		%\hspace{2.5cm}\begin{minipage}[t]{7em}
		%	\vspace{-2cm}
		%	\noindent\\
		%	\vspace{-0.5ex}\hspace{0.105cm}
		%\end{minipage}

	}{ %Title (centered top)
		{%\vspace{0pt}\hspace{1cm} \
			{\titlefont \scshape{A finite-state morphological analyser for Tuvan}
			}
		}
	}{ %Authors (centered top, below title)
		\vspace{-0.6em}
		\begin{center}
			\begin{minipage}[t]{9em}
				\begin{spacing}{0.4}
				{Francis M.\ Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{12em}
				\begin{spacing}{0.4}
					{Jonathan North Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{9em}
				\begin{spacing}{0.4}
					{Aziyana Bayyr-ool}\\
					{\footnotesize XXX\\\texttt{yyy@xxx}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\includegraphics[height=6.25em]{iu_tab-crop}
		\hspace{2.5cm}\includegraphics[angle=90,height=6.8em]{apertium5b}%\hspace{-2em}
	}

>>>>

	\begin{poster}{
		grid=false,
		%eyecatcher=false,
		borderColor=bordercol,
		headerColorOne=iumidnight,
		headerColorTwo=iumidnight,
		%headerColorOne=blue,
		headerFontColor=white,
		% Only simple background color used, no shading, so boxColorTwo isn't necessary
		boxColorOne=boxcolor,
		headershape=roundedright,
		headerborder=open,
		headerheight=0.1\textheight,
		%headershape=roundedright,
		%headershade=plain,
		%headerfont=\Large\textsf, %Sans Serif
		%headerfont=\Large\sf\bf,
		textborder=rectangle,
		%background=plain,
		%background=user,
		background=none,
		headerborder=open,
		boxshade=plain,
		textborder=roundedleft,
		columns=4,
	}{ %Eye Catcher, empty if option eyecatcher=false - unused
		\includegraphics[height=6.4em]{uitlogo}
		\includegraphics[height=6.2em]{iu_tab-crop}
		%\hspace{2.5cm}\begin{minipage}[t]{7em}
		%	\vspace{-2cm}
		%	\noindent\\
		%	\vspace{-0.5ex}\hspace{0.105cm}
		%\end{minipage}

	}{ %Title (centered top)
		{%\vspace{0pt}\hspace{1cm} \
			{\titlefont \scshape{A finite-state morphological analyser for Tuvan}
			}
		}
	}{ %Authors (centered top, below title)
		\vspace{-0.6em}
		\begin{center}
			\begin{minipage}[t]{5.75em}
				\begin{spacing}{0.4}
				{Francis Tyers}\\
				{\footnotesize UiT Norgga Árktalaš Universitehta \\\texttt{francis.tyers@uit.no}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{9.25em}
				\begin{spacing}{0.4}
					{Jonathan Washington}\\
					{\footnotesize Indiana University\\\texttt{jonwashi@indiana.edu}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{8em}
				\begin{spacing}{0.4}
					{Aziyana Bayyr-ool}\\
					{\footnotesize Сибирское отделение Российской академии наук\\\texttt{azikoa@mail.ru}}
				\end{spacing}
			\end{minipage}
			\begin{minipage}[t]{6em}
				\begin{spacing}{0.4}
					{Aelita Salchak}\\
					{\footnotesize Тываның Күрүне Университеди\\\texttt{aelita\_74@mail.ru}}
				\end{spacing}
			\end{minipage}
		\end{center}
	}{ %More eye catchers, on the right side
		\includegraphics[height=6.2em]{img/Tuvsu}
		\includegraphics[height=6.2em]{img/soranif}
		%\hspace{2.5cm}
		\includegraphics[angle=90,height=6.7em]{apertium5b}%\hspace{-2em}
	}
